The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-23 Discussion/lessons.tex
edits to discussion section

\subsection{Lessons Learned}
    From our results, it is evident that the vulnerability exists in the wild. Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 14,875,413 websites - a pretty significant number. We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

    After analyzing the results, we would like to make a few more observations. We believe that one of the reasons for the small percentage of occurrence (compared to SQL Injection or XSS), can be attributed to what we like to call the `car parking analogy'.
    The car parking analogy is something like this: Imagine that we are parking a car on a road that is prone to attacks by thieves. Now, if all the cars were unlocked, the car that is most likely to get stolen is quite unsurprisingly the most expensive one or the one that is easiest to get away with.

    Now imagine the same thing on the World Wide Web: we have websites that can each have multiple vulnerabilities. Now, it makes sense for an attacker to try and attack websites with more widespread vulnerabilities such as SQL Injection or XSS, rather than attempt to exploit E-Mail Header Injection, seeing as this requires a more concentrated effort, with carefully crafted payloads and a waiting time for the e-mail to be delivered. SQL Injection attacks and XSS attacks are also better documented, with well-known attack vectors, and automated tools to help detect the presence of these vulnerabilities on websites.

    This also gives more incentive for the website developer to add protection against attacks such as SQL injection and XSS. The developer might then (possibly with the help of a sanitization library) sanitize the user input and remove \emph{all} special characters, including the newline characters (\textbackslash{}n, \textbackslash{}r), which adversely affects E-Mail Header Injection attacks.

	We come to this conclusion because of our discovery of the \texttt{To header injection}. Clearly, this is possible due to incomplete sanitization performed by the application. We suspect that this incomplete sanitization is actually sanitization that is performed for some other vulnerability, and not specifically for E-Mail Header Injection attacks. We would also like to remark that \texttt{To header injection} is not complete E-Mail Header Injection, but only a special subset.

    Thus, indirectly, this kind of protection against other attacks affects the attempts to perform E-Mail Header Injection. However, this does not completely negate the attempts if the checks are only on the client-side. Also, even with server-side validation, often, the only input fields that are validated are ones that are either inserted into the database (SQL Injection) and the ones that are displayed to the user as part of the web site (XSS).

	A second and a far more common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the websites. CAPTCHAs pose a very difficult problem for our system to exploit E-Mail Header Injection, even if it is present.

	This does not mean that the vulnerability is not a large threat. In fact, this vulnerability can also have some major consequences, the least of which can be spamming and phishing attacks.
	In today's digital world, identity theft has become all the more common. E-Mail Header Injection provides attackers with the ability to easily extract information about users, not just from a server, but from the user himself, by sending him fake messages that look extremely authentic, since these messages are sent by the mail server of the website itself.

    From our research, we found two different forms of the E-Mail Header Injection Vulnerability: the first one is the traditional one, where we are able to inject any header into the forms, allowing us complete control over the contents of the e-mail. We identify this with the presence of both the \texttt{bcc} header and the \texttt{x-check} header. This is the most potent form of the vulnerability and is found on quite a few websites. This is also the vulnerability that is documented and discussed on many websites.

    The second attack is an interesting one, as this has not yet been documented, and provides the ability to inject multiple e-mail addresses into only the \texttt{To} field. We christened this as \texttt{To header injection}. In this form of the vulnerability, we are able to simply add addresses to the \texttt{To} field of the form with newlines separating the e-mail addresses. Whether this particular form of the vulnerability is found due to the websites in question, or whether this is an implementation issue with a particular language or framework, is unclear. However, from our preliminary analysis, it is evident that these websites do not share much with respect to the languages and frameworks used. 
    Even in this form of the attack, we are still able to extract information that should be private to a given user, and in some of these cases, able to inject enough data to spoof the first few lines of the e-mail message. From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 163 forms, while spoofing using \texttt{To header injection} was possible on 13 forms.

    While not being as impactful as the primary vulnerability, this form of the vulnerability does still provide the ability to send e-mails to multiple recipients, and can easily result in information leakage or spam generation on a large scale.

>>>>

\subsection{Lessons Learned}
From our results, it is evident that \ehi vulnerabilities exist in the wild.
% Adam: Sai, I don't understand this math. The 1.46% number is calculated based on the number of forms we were able to fuzz with a malicious payload. This isn't the same as the number of websites. But, using 673/21675680 is not good either because that is # of URLs and it seems like the number you have here is websites. What we need is what % of *websites* (probably estimated as domains) did we find to be vulnerable out of *all* websites/domains that we found. When we use this number, we need to be clear what it is that we are using.
Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we consider total number of websites on the World Wide Web--- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016---and calculate \successDelta\ percent (the occurrence rate of \ehi vulnerability as found by our system) of that number, this yields 14,875,413 websites. Of course, extrapolation in this way is not an accurate measure of the prevalence of \ehi vulnerabilities. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

%% We believe that one of the reasons for the small percentage of occurrence (compared to SQL Injection or Cross-Site Scripting), can be attributed to what we like to call the `car parking analogy'.
%%     The car parking analogy is something like this: Imagine that we are parking a car on a road that is prone to attacks by thieves. Now, if all the cars were unlocked, the car that is most likely to get stolen is quite unsurprisingly the most expensive one or the one that is easiest to get away with.

%%     Now imagine the same thing on the World Wide Web: we have websites that can each have multiple vulnerabilities. Now, it makes sense for an attacker to try and attack websites with more widespread vulnerabilities such as SQL Injection or XSS, rather than attempt to exploit E-Mail Header Injection, seeing as this requires a more concentrated effort, with carefully crafted payloads and a waiting time for the e-mail to be delivered. SQL Injection attacks and XSS attacks are also better documented, with well-known attack vectors, and automated tools to help detect the presence of these vulnerabilities on websites.

%%     This also gives more incentive for the website developer to add protection against attacks such as SQL injection and XSS. The developer might then (possibly with the help of a sanitization library) sanitize the user input and remove \emph{all} special characters, including the newline characters (\textbackslash{}n, \textbackslash{}r), which adversely affects E-Mail Header Injection attacks.

%% 	We come to this conclusion because of our discovery of the \texttt{To header injection}. Clearly, this is possible due to incomplete sanitization performed by the application. We suspect that this incomplete sanitization is actually sanitization that is performed for some other vulnerability, and not specifically for E-Mail Header Injection attacks. We would also like to remark that \texttt{To header injection} is not complete E-Mail Header Injection, but only a special subset.

%%     Thus, indirectly, this kind of protection against other attacks affects the attempts to perform E-Mail Header Injection. However, this does not completely negate the attempts if the checks are only on the client-side. Also, even with server-side validation, often, the only input fields that are validated are ones that are either inserted into the database (SQL Injection) and the ones that are displayed to the user as part of the web site (XSS).

% Adam: Please add a citation to a CAPTCHA paper
	A common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the web applications. CAPTCHAs pose a very difficult problem for our system to exploit \ehi, even if it is present.

	%% This does not mean that the vulnerability is not a large threat. In fact, this vulnerability can also have some major consequences, the least of which can be spamming and phishing attacks.
	%% In today's digital world, identity theft has become all the more common. E-Mail Header Injection provides attackers with the ability to easily extract information about users, not just from a server, but from the user himself, by sending him fake messages that look extremely authentic, since these messages are sent by the mail server of the website itself.

    We found two different forms of \ehi: the first one is the traditional one, injecting any header into the \email that allows the attacker complete control over the contents of the \email. 
The second attack has not yet been documented and provides the ability to inject multiple \email addresses into the \texttt{To} field. We call this a \texttt{To header injection}. In this  vulnerability, an attacker can add addresses to the \texttt{To} field of the email with newlines separating the \email addresses. We could not determine if this vulnerability is due to unique flaws in each web application or if this vulnerability is due to an implementation issue with a particular language or framework. However, from our preliminary analysis, it is evident that the vulnerable web applications do not share much in common.

\texttt{To header injection} allows an attacker to extract information that should be private,
% Adam: It's not clear what this means that we have enough data to spoof the few lines of the message. I thought to header injection just controls the TO field, not the message contents. 
and in some of these cases, able to inject enough data to spoof the first few lines of the \email message. From Table~\ref{tab:analysis}, information leakage using \texttt{To header injection} was possible on 163 forms, while spoofing using \texttt{To header injection} was possible on 13 forms.

    %% While not being as impactful as the primary vulnerability, this form of the vulnerability does still provide the ability to send \emails to multiple recipients, and can easily result in information leakage or spam generation on a large scale.

### 2016-05-23 Discussion/limits.tex
edits to discussion section

\subsection[Limitations]{Limitations of the Project}
\label{limitations}
	This section discusses the limitations of our project. The following list, although not exhaustive, goes into some of them in detail:
	\begin{itemize}
		\item Bot Blockers and CAPTCHAs\\
		Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.,\ mechanisms built-in to a website to prevent automated crawls or form submissions. Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3}, \cite{captchas2}.

		We have made sure that we do not affect hidden fields in the form, however, despite considerable research in breaking CAPTCHAs~\cite{captchas2}, \cite{captchas} and although not impossible to break, breaking CAPTCHAs remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.

		\item JavaScript Apps - Due to the growing emphasis on responsive web applications, more and more single-page web applications are being built purely with JavaScript. Even conventional applications are now making use of JavaScript to dynamically insert content and update the pages. This means that these dynamically injected components are not a part of the initial source code that is sent to the client by the server.

		Thus, our system never receives dynamically injected forms from the server and hence is unable to detect whether these vulnerabilities are present in such forms. The only workaround would be, to use a JavaScript engine to query for the \texttt{document.getElementsByTagName('html')[0].innerHTML} (from inside web browser automation tools like Selenium, etc.), and then use that as the source code for our URL.

		Since this would add unnecessary bulk and complexity to our application, we chose not to do it, and thus, we consider this to be a limitation.

		\item Blacklisting by websites and ISPs\\
		During the actual crawl, our system was blacklisted by a few websites (mostly WordPress ones), and Internet Service Providers (ISPs).
		To overcome this, we did two things:
		\begin{enumerate}
			\item Used an IP range of 60 different IP addresses.
			\item Used a blacklist of our own to prevent our Fuzzer from fuzzing websites that are known to blacklist automated crawlers.  The result was that we could not gather any data about these websites.
		\end{enumerate}

		\item Blogs powered by WordPress/Drupal\\
		We found that certain WordPress plugins prevent the E-Mail Header Injection attack by sanitizing user input on contact forms. Some of these plugins are discussed in the following section. Although not all websites built with WordPress are secure from the attack, between the presence of the plugins on some websites, and getting tagged as `spambots' by others, we were able to do vulnerability analysis on few sites powered by WordPress.

		\item E-Mail libraries\\
        E-Mail libraries like the PHP Extension and Application Repository's (PEAR) mail library provide sanitization checks for user input. While this is technically not a limitation of our project, it still makes it such that we are not able to inject these sites successfully.
        A few other libraries for each language are discussed in the following section.

        \item Websites that are not in English\\
        Because we are only searching for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, if the website does not use English names for its forms, our system will not be able to find the presence of an e-mail field. An example is shown in Listing~\ref{code:htmlfrench}. Here, the French word for \texttt{e-mail} --- courrier électronique --- is used, and our system is unable to find the presence of the e-mail form.

        \item Handling Malformed HTML\\
        The parser that we use for HTML parsing --- Beautiful Soup --- does not try to parse malformed HTML, and throws an exception on encountering malformed content. Thus, we have designed the system to exit gracefully on such occasions. A side-effect of this is that our system is unable to parse websites with bad markup\,\footnotemark.

        \footnotetext{We do not have any data about whether bad markup indicates an overall lower quality of the website, and thus cannot comment on whether such websites are more likely to have vulnerabilities, although the author strongly suspects that that might be the case.}

        \item Black-box Testing\\
        The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section~\ref{sys:appr}. However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers). We have to manually e-mail the developers to get this feedback.

       	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
       	As discussed in Section~\ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}. This might result in a false positive in certain forms, like the one shown in Listing~\ref{code:false_positive}.

       	\begin{lstlisting}[language=HTML,caption={E-Mail field checker
              - false positives, the system incorrectly classifies
              this as an e-mail form.},label={code:false_positive}, float]
<form method="post">
E-Mail us if you have any questions!!
<input type="text" name="query"><br>
<input type="submit" value="Search">
</form>
       	\end{lstlisting}

       	The word \texttt{E-Mail} on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not. However, as we will see, this is not really a significant issue, as despite being added to the \texttt{email\_forms} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form. We chose to go with this design, as it allows us to detect almost every form that provides the capability to send or receive e-mail.
	\end{itemize}

>>>>

\subsection[Limitations]{Limitations}
\label{limitations}

		Because our system is fully automated, it is also susceptible to being stopped by mechanisms in web applications that prevent automated crawls or form submissions. Measures such as CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3, captchas2}.

		We made sure that we do not fuzz hidden fields in the form, however, despite considerable active research in breaking CAPTCHAs~\cite{captchas2, captchas}, breaking CAPTCHAs remains out of the scope of this project.

	   Due to the growing emphasis on responsive web applications, more and more web applications are being built with only client-side  JavaScript. Even conventional web applications use JavaScript to dynamically insert content and update the pages. This trend means that these dynamically injected HTML components are not part of the initial HTML that is sent to the client by the server.

		Thus, our system will not see dynamically injected forms and hence is unable to detect whether \ehi vulnerabilities are present in these forms. The workaround would be to use a JavaScript engine to query for the \texttt{document.getElementsByTagName('html')[0].innerHTML} (from inside web browser automation tools such as Selenium), then use that as the source HTML. We chose not to do this for performance reasons.

		During the crawl, our system was blacklisted by a few web applications (mostly WordPress ones), and Internet Service Providers (ISPs).
		To overcome this, we did two things:
		\begin{enumerate}
			\item Used an IP range of 60 different IP addresses.
			\item Used a blacklist of our own to prevent our Fuzzer from fuzzing web application that are known to blacklist automated crawlers.  However, we could not gather any data about these web applications.
		\end{enumerate}

		We found that certain WordPress plugins prevent the \ehi attack by sanitizing user input on contact forms. Although not all  WordPress web applications are secure, between the presence of the plugins on some websites, and getting tagged as ``spambots'' by others, we found few vulnerabilities on WordPress web applications.

        E-Mail libraries such as the PHP Extension and Application Repository's (PEAR) mail library provide sanitization for user input. While this is not strictly a limitation of our project, it still means that we are not able to inject sites that used these libraries successfully.

        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field. An example is shown in Listing~\ref{code:htmlfrench}. Here, the French word for \texttt{e-mail}---courrier électronique---is used, and our system is unable to find the presence of the e-mail form.

        The parser that we use for HTML parsing---Beautiful Soup---does not parse malformed HTML and throws an exception on encountering malformed HTML. Thus, we have designed the system to exit gracefully on such occasions. A side-effect of this is that our system is unable to test web applications with bad HTML markup\,\footnotemark.

        \footnotetext{We do not have any data about whether bad markup indicates an overall lower quality of the web application, and thus cannot comment on whether such websites are more likely to have vulnerabilities.}

        Black-box testing is highly beneficial as explained in Section~\ref{sys:appr}, however it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers). We must manually notify the developers to get this feedback.

%%        	As discussed in Section~\ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}. This might result in a false positive in certain forms, like the one shown in Listing~\ref{code:false_positive}.

%%        	\begin{lstlisting}[language=HTML,caption={E-Mail field checker
%%               - false positives, the system incorrectly classifies
%%               this as an e-mail form.},label={code:false_positive}, float]
%% <form method="post">
%% E-Mail us if you have any questions!!
%% <input type="text" name="query"><br>
%% <input type="submit" value="Search">
%% </form>
%%        	\end{lstlisting}

%%        	The word \texttt{E-Mail} on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not. However, as we will see, this is not really a significant issue, as despite being added to the \texttt{email\_forms} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form. We chose to go with this design, as it allows us to detect almost every form that provides the capability to send or receive e-mail.

### 2016-05-23 Discussion/mitigation.tex
chap6,7,8 prelim edits
Edited through the results section
edits to discussion section

\subsection[Mitigation Strategy]{How to prevent this attack}
\label{disc:mitigation}
This section describes the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
\begin{itemize}
	\item Use Mail Libraries\\
	This is the preferred way of combating this vulnerability. Using a library that is well tested can remove the burden of input sanitization from the developer. Also, since most of these libraries are open-source, bugs are identified quicker and fixes are readily available.
	A list of known secure libraries for each popular language and framework is shown in Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of E-Mail Header Injection vulnerability.
	\begin{table}[!htbp]
		\centering
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	\item Use a Content Management System (CMS) \\
	Content management systems like WordPress and Drupal include certain libraries and plugins to prevent E-Mail Header Injection. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the right E-Mail plugins when using such CMS', as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

	\item Input Validation\\
	If neither of the two options above is feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization. Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.

	Client Side validation alone is not sufficient, and must be supplemented by server-side validation to mitigate the attack. Constant updates to validation methods are required so that new attack vectors do not harm the website in any way.
	Test driven development for such validation methods is also encouraged so that we can be reasonably sure of our defense mechanisms.
\end{itemize}

>>>>

\subsection{Mitigation Strategy}
\label{disc:mitigation}
After demonstrating that \ehi vulnerabilities exist on the web at large, we now describe the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
\begin{itemize}
	\item Use Mail Libraries\\
	Using a safe \email library is the preferred way of preventing \ehi vulnerabilities. Using a library that is well tested can remove the burden of input sanitization from the developer. 
	A list of known secure libraries for each language and framework discussed previously is shown in Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of \ehi vulnerability.
	\begin{table}[tbp]
		\centering
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	\item Use a Content Management System (CMS) \\
	Content management systems such as WordPress and Drupal include libraries and plugins to prevent \ehi. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the correct \email plugin, as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

	\item Input Validation\\
	If neither of the two options are feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization. Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.

	%% Client Side validation alone is not sufficient, and must be supplemented by server-side validation to mitigate the attack. Constant updates to validation methods are required so that new attack vectors do not harm the website in any way.
	%% Test driven development for such validation methods is also encouraged so that we can be reasonably sure of our defense mechanisms.
\end{itemize}

### 2016-05-23 System/assumptions.tex
edits to discussion section

\subsection{Assumptions}
In addition to the limitations that were already discussed, we made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
\begin{enumerate}
	\item \textbf{Crawler is not blocked by firewalls}\\
	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is almost impossible to set our system up.

	\item \textbf{The Crawler feed is an ideal representation of the World Wide Web} \\
	This is a reasonable expectation, albeit an unrealistic one.

@@

	However, this assumption is reasonable due to the `Law of averages'~\cite{wiki:Law_of_averages}, the `Law of big numbers'~\cite{wiki:Law_of_large_numbers}, and the concept of `Regression to the mean'~\cite{wiki:Regression_toward_the_mean}. Simply stated, a crawl of this large magnitude should give us a very distributed sample of the overall Web, eventually converging to the average of all websites in existence.

	\item \textbf{Injection of \texttt{bcc} indicates the existence of E-Mail Header Injection Vulnerability} \\
	We assume that the ability to inject a \texttt{bcc} header field is proof that the E-Mail Header Injection vulnerability exists in the application. We do not inject any additional payloads that can modify the subject, message body, etc.\ as this analysis is designed to be as benign as possible.
	We believe that this is a reasonable assumption, as altering e-mail headers is a goal of exploiting E-Mail Header Injection vulnerability.
\end{enumerate}

That concludes our discussion about the design of the system. To recap, we discussed our approach, the system architecture and how the components fit into our architecture. We also discussed the issues faced, and the assumptions that we made while building the system. %The next section describes, in brief, the experimental setup we used for our system.

>>>>

\subsection{Assumptions}
In addition to the limitations that were already discussed, we made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
\begin{enumerate}
	\item \textbf{The crawler is not blocked}\\
	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is impossible to discover vulnerabilities.

	\item \textbf{The Crawler feed is an ideal representation of the World Wide Web} \\

	This is a reasonable expectation, albeit an unrealistic one.

@@

	However, this assumption is reasonable due to the ``Law of averages''~\cite{wiki:Law_of_averages}, the ``Law of big numbers''~\cite{wiki:Law_of_large_numbers}, and the concept of ``Regression to the mean''~\cite{wiki:Regression_toward_the_mean}. Simply stated, a crawl of this magnitude should provide a distributed sample of the overall Web, eventually converging to the average of all web applications in existence.

	\item \textbf{Injection of \texttt{bcc} indicates the existence of an \ehi Vulnerability} \\
	We assume that the ability to inject a \texttt{bcc} header field is proof that the \ehi vulnerability exists in the application. We do not inject any additional payloads that can modify the subject, message body, etc., as our analysis is designed to be as benign as possible.
	We believe that this is a reasonable assumption, as altering e-mail headers is a goal of exploiting \ehi vulnerability.
\end{enumerate}
